Extracting Angular Observables without a Likelihood\\and Applications to Rare Decays

### 2014-08-04 draft.tex
[sec. I,II] Connect to moments literature, compare likelihood and moments methods

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor}
\usepackage{hepparticles}
\usepackage{hepnicenames}
\usepackage{hepunits}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{epstopdf}
%% Shortcuts %%
\newcommand{\rmdx}[1]{\mbox{d} #1 \,} % differential
\newcommand{\refapp}[1]{app.~(\ref{app:#1})}
\newcommand{\refeq}[1]{eq.~(\ref{eq:#1})}
\newcommand{\refsec}[1]{sec.~(\ref{sec:#1})}
\newcommand{\reftab}[1]{tab.~(\ref{tab:#1})}
\newcommand{\ie}{\textit{i.e.}}
\newcommand{\nuvec}{\vec{\nu}}
\newcommand{\thvec}{\vec{\vartheta}}
\let\oldtheta\theta
\renewcommand{\theta}{\vartheta}
%\newcommand{\GeV}{\text{GeV}}
\newcommand{\order}[1]{\mathcal{O}\left({#1}\right)}
\let\eps\varepsilon
\newcommand{\aver}[1]{\langle #1 \rangle}
\newcommand{\est}[1]{\widehat{#1}}
\newcommand{\wwhat}[1]{\widehat{\widehat{#1}}}
\DeclareMathOperator{\cov}{Cov}
%\DeclareMathOperator{\skew}{Skew}
\DeclareMathOperator{\kurt}{Kurt}

@@

We continue with basic definitions that pertain to angular observables, and our
results in the subsequent sections. Let $\thvec = (\theta_1, \dots \theta_N)$ denote the set of all
angles, and let $\nuvec = (\nu_1, \dots \nu_M)$ denote the set of all
other non-angular kinematic variables needed to fully specify the
final state of the process under study. For example, $\nuvec$ may
include invariant masses or center-of-mass energies. We define an
angular observable $S_i$ as a coefficient in the probability density
function (PDF) of the process by means of
\begin{align}
    \label{eq:def-P}
    P(\nuvec, \thvec) \equiv \sum_i S_i(\nuvec) \times f_i(\thvec)\,.
\end{align}
Here, the dependence on the $n$ decay angles $\thvec$ has been
explicitly factored out in terms of the angular functions
$\{f_i(\thvec)\}$, which we assume to fulfill the orthonormality relations
\begin{equation}
    \label{eq:def-ortho-rel}
    \int_\Omega \rmdx{^N \theta} f_i(\thvec) f_j(\thvec)  = \delta_{ij}\,,
\end{equation}
with $\Omega$ representing the full angular phase space relevant to the process.
For the purpose of this letter, however, it suffices that the system
of angular functions $\{f_i(\thvec)\}$ can be transformed into an
orthonormal basis. The transformation needs to be worked out on a
case-by-case basis. For a selection of $B$ decays which we consider the most interesting
we list the transformations in a series of appendices \ref{app:btokll} through
\ref{app:lambdabtolambdall}.\\

For particle decays, $P$ is generally expressed in terms of the fully differential decay width,
\begin{align}
    \label{eq:def-P-decay}
    P(\nuvec, \thvec) \equiv \frac{1}{\Gamma}\frac{\rmdx{^{N+M}\Gamma}}{\rmdx{\nu_1} \dots \rmdx{\nu_M} \rmdx{\theta_1} \dots \rmdx{\theta_N}}\,,
\end{align}
where $\Gamma$ is the total decay width. For a scattering process, one can similarly use
\begin{align}
    \label{eq:def-P-scattering}
    P(\nuvec, \thvec) \equiv \frac{1}{\sigma}\frac{\rmdx{^{N+M}\sigma}}{\rmdx{\nu_1} \dots \rmdx{\nu_M} \rmdx{\theta_1} \dots \rmdx{\theta_N}}\,,
\end{align}
where the total cross section $\sigma$ is used for the
normalization. Since the determination of the total decay width or
total cross section can be quite difficult, we emphasize that
different normalizations for $P$ can be used.  For instance, the total
decay width (or cross section) of the process of interest can be
replaced by the corresponding quantity of a control-channel
process. This change of normalization is equivalent to a linear rescaling of
the angular observables $\lbrace S_i\rbrace$; thus ratios or similar suitable combinations
of the angular observables are invariant.\\

% Our method is closely related to Pearson's method of moments
% \citeneeded{}. One draws samples from a PDF $P(x | \nuvec)$ that
% depends on parameters $\nuvec$. Then one approximates the population
% (central) moments $x^k$ by the sample moments
Our method is an extension of the classical method of moments with
orthogonal functions~\cite{James:2006zz}.

@@

The orthonormality relations \refeq{def-ortho-rel} imply that a single angular observable $S_i$
can be projected out of the full PDF $P$ by means of
\begin{equation}
    \label{eq:det-Pi-analytical}
    S_i(\nuvec) = \int_{\Omega} \rmdx{^N \theta} \hat{f}_i(\thvec) P(\nuvec, \thvec)\,.
\end{equation}
where $\lbrace \hat{f}_i \rbrace$ denotes a \emph{dual basis} of angular function. In all generality
the bases $\lbrace f_i \rbrace$ and $\lbrace \hat{f}_i \rbrace$ are not identical. This is the
case for our selection of applications in appendices \ref{app:btokll} through \ref{app:lambdabtolambdall}.\\

It is sensible to refer to the angular observable $S_i$ as the \emph{$\hat{f}_i$-moment} of the PDF $P$.
We emphasize that a relation of type \refeq{det-Pi-analytical} holds for any combination of
scalar product and orthonormal basis of angular functions $\lbrace f_i \rbrace$; \ie, there is no unique
basis of angular functions. For the proof we refer to ref. \cite{Dighe:1998vk}.\\
In addition, integration over the non-angular variables yields
\begin{equation}
    \langle S_i\rangle
    \equiv \int \rmdx{^M \nu} S_i(\nuvec)
    = \int \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N \theta}\hat{f}_i(\thvec) P(\nuvec,\thvec) \right].
\end{equation}
The remainder of this section describes the method of moments, in which we replace the
analytical integration \refeq{det-Pi-analytical} by Monte Carlo (MC) estimators.\\

The central tenet of MC integration is the fact that the expectation value $E_P[g]$ of some function
$g(x)$ under the probability density $P(x)$,
\begin{equation}
    E_P[g] \equiv \int \rmdx{x} g(x) P(x)
\end{equation}
can be approximated \cite{MCSM-2004} by an MC estimator $\est{E_P[g]}$
\begin{equation}
    \label{eq:mc-id}
    E_P[g] \to \widehat{E_P[g]} \equiv \frac{1}{K} \sum_{k=1} g(x^{(k)})
\end{equation}
due to the strong law of large numbers for $K \to \infty$ assuming
that the variates $x^{(k)}$, $k = 1, \dots, K$ are distributed as
$P$; i.e.,
\begin{equation}
    x^{(k)} \sim P\,.
\end{equation}
Throughout this letter we denote all MC estimators with a wide hat.\\

Application of \refeq{mc-id} then yields
\begin{equation}
    \langle S_i\rangle \to \widehat{\langle S_i\rangle} = \frac{1}{K} \sum_{k=1}^{K} \hat{f}_i(x^{(k)})\,.
\end{equation}
It is often of interest to obtain the $\nuvec$- observables integrated
over certain ranges of $\nuvec$; i.e., binned measurements of $\langle
S_i\rangle$.
Therefore, we introduce the bin-integrated quantity
\begin{align}
    \langle S_i\rangle_{\vec{a},\vec{b}}
    & = \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} S_i(\nuvec)\\
    & = \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta} \hat{f}_i(\thvec) P(\nuvec,\thvec)  \right]\\
    & = \int \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta} \hat{f}_i(\thvec) P(\nuvec,\thvec)
        \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,
        \right],
\end{align}
where the argument of the indicator function $ \mathbf{1}(\vec{a} \le
\nuvec \le \vec{b})$ is to be interpreted componentwise.
Application of \refeq{mc-id} immediately yields
\begin{equation}
    \label{eq:bin-importance}
    \widehat{\langle S_i\rangle_{\vec{a},\vec{b}}}
    = \frac{1}{K} \sum_{k=1}^{K} \hat{f}_i(x^{(k)})         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
\end{equation}
This basically reduces the estimation of
$\aver{S_i}_{\vec{a},\vec{b}}$ to a (weighted) counting experiment. In
the limit $N \to \infty$, the random vector $( \dots,
\aver{S_i}_{\vec{a},\vec{b}}, \dots)$ follows a multivariate Gaussian
distribution \citeneeded\fred{Robert,Casella?}
with the mean vector estimated by \refeq{bin-importance}, and the covariance
estimated as
\begin{equation}
    \cov[\aver{S_i},\aver{S_j}]_{\vec{a},\vec{b}} \to \est{\cov}[\aver{S}_i, \aver{S}_j]_{\vec{a},\vec{b}}
        = \frac{1}{K - 1} \sum_{k=1}^{K} \big[\hat{f}_i(x^{(k)}) - \est{\langle S_i\rangle_{\vec{a},\vec{b}}}\big]\,\big[\hat{f}_j(x^{(k)}) - \widehat{\langle S_j\rangle_{\vec{a},\vec{b}}}\big]
        \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
\end{equation}
We would like to emphasize that the sample covariance should rapidly converge towards the true covariance matrix.
We propose to declare convergence once estimators for skewness and kurtosis are sufficiently small,
\begin{equation}
    \est{\operatorname{Skew}}[\aver{S_i},\aver{S_j}] \ll 1\,\,\text{ and }\,\,\est{\kurt}[\aver{S_i},\aver{S_j}] \ll 1\,.
\end{equation}

The convergence towards a normal distribution for the results allows to transfer correlation information to interested
theorists. In particular, this will allow to constrict predictive distributions of optimized observables.
(See e.g. \cite{Egede:2008uy,Egede:2010zc,Bobeth:2010wg,Becirevic:2011bp,Bobeth:2012vn,Matias:2012xw,DescotesGenon:2012zf}
for definitions of such optimized observables in $B\to K^*\ell^+\ell^-$ decays, \cite{Faller:2013dwa} for application to
the decay $B\to \pi\pi\ell^-\bar\nu_\ell$, and \cite{Boeer:2014xx} for observables in $\Lambda_b\to\Lambda(\to N\pi)\ell^+\ell^-$).

@@

The dual basis $\lbrace \hat{f}_i\rbrace$ reads
\begin{equation}
\begin{aligned}
    \hat{f}_1 & = \frac{9}{8} - \frac{15}{8}\cos^2\theta_1\,, &
    \hat{f}_2 & = \frac{3}{2}\cos\theta_1\,, &
    \hat{f}_3 & = -\frac{15}{8} + \frac{45}{8}\cos^2\theta_1\,,
\end{aligned}
\end{equation}
such that
\begin{equation}
    \int_0^\pi \rmdx{\theta_1} \hat{f}_i(\theta_1) P(q^2, \theta_1) = S_i(q^2)\,.
\end{equation}

@@

The dual basis reads
\begin{equation}
\begin{aligned}
    \hat{f}_{1s} & = \frac{\big( 63 \sin^2\theta_2 - 42 \cos^2\theta_2\big) + \big(  45 \sin^2\theta_2 - 30 \cos^2\theta_2\big)\cos 2\theta_1}{64} \,,\\
    \hat{f}_{1c} & = \frac{\big(-21 \sin^2\theta_2 + 84 \cos^2\theta_2\big) + \big( -15 \sin^2\theta_2 + 60 \cos^2\theta_2\big)\cos 2\theta_1}{32} \,,\\
    \hat{f}_{2s} & = \frac{\big( 45 \sin^2\theta_2 - 30 \cos^2\theta_2\big) + \big(+135 \sin^2\theta_2 - 90 \cos^2\theta_2\big)\cos 2\theta_1}{64} \,,\\
    \hat{f}_{2c} & = \frac{\big(-15 \sin^2\theta_2 + 60 \cos^2\theta_2\big) + \big( -45 \sin^2\theta_2 +180 \cos^2\theta_2\big)\cos 2\theta_1}{32} \,,
\end{aligned}
\end{equation}
as well as
\begin{equation}
\begin{aligned}
    \hat{f}_{1i} & = \frac{\big(21 + 15 \cos1\theta_2\big)\cos\theta_2}{16}               \,,&
    \hat{f}_{2i} & = \frac{\big(15 + 45 \cos1\theta_2\big)\cos\theta_2}{16}               \,,\\
    \hat{f}_{3}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \cos2\theta_3}{32}                \,,& &\\
    \hat{f}_{4}  & = \frac{75 \sin 2\theta_2 \sin 2\theta_1 \cos \theta_3}{32}                \,,&
    \hat{f}_{4i} & = \frac{15 \sin  \theta_2 \sin 2\theta_1 \cos \theta_3}{8}                 \,,\\
    \hat{f}_{5}  & = \frac{15 \sin 2\theta_2 \sin  \theta_1 \cos \theta_3}{8}                 \,,&
    \hat{f}_{5i} & = \frac{3  \sin  \theta_2 \sin  \theta_1 \cos \theta_3}{2}                 \,,\\
    \hat{f}_{6s} & = \frac{\big( 9\sin^2\theta_2 -  6 \cos^2\theta_2\big)\cos\theta_1}{4} \,,&
    \hat{f}_{6c} & = \frac{\big(-3\sin^2\theta_2 + 12 \cos^2\theta_2\big)\cos\theta_1}{2} \,,\\
    \hat{f}_{7}  & = \frac{15 \sin 2\theta_2 \sin  \theta_1 \sin \theta_3}{8}                 \,,&
    \hat{f}_{7i} & = \frac{3  \sin  \theta_2 \sin  \theta_1 \sin \theta_3}{2}                 \,,\\
    \hat{f}_{8}  & = \frac{75 \sin 2\theta_2 \sin 2\theta_1 \sin \theta_3}{32}                \,,&
    \hat{f}_{8i} & = \frac{15 \sin  \theta_2 \sin 2\theta_1 \sin \theta_3}{8}                 \,,\\
    \hat{f}_{9}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \sin2\theta_3}{32}                \,.\\
\end{aligned}
\end{equation}
such that
\begin{equation}
    \int_0^\pi \rmdx{\theta_1} \int_0^\pi \rmdx{\theta_2} \int_0^{2\pi} \rmdx{\theta_3} \hat{f}_k(\theta_1,\theta_2,\theta_3) P(q^2, \theta_1,\theta_2,\theta_3) = S_k(q^2)\,.
\end{equation}

>>>>

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor}
\usepackage{hepparticles}
\usepackage{hepnicenames}
\usepackage{hepunits}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{epstopdf}

%% Shortcuts %%
\newcommand{\aver}[1]{\langle #1 \rangle}
\newcommand{\dual}[1]{\tilde{#1}}
\newcommand{\est}[1]{\widehat{#1}}
\newcommand{\ie}{\textit{i.e.}}
\newcommand{\nuvec}{\vec{\nu}}
\newcommand{\order}[1]{\mathcal{O}\left({#1}\right)}
\newcommand{\refapp}[1]{app.~(\ref{app:#1})}
\newcommand{\refeq}[1]{eq.~(\ref{eq:#1})}
\newcommand{\refsec}[1]{sec.~(\ref{sec:#1})}
\newcommand{\reftab}[1]{tab.~(\ref{tab:#1})}
\newcommand{\rmdx}[1]{\mbox{d} #1 \,} % differential
\newcommand{\thvec}{\vec{\vartheta}}
\let\oldtheta\theta
\renewcommand{\theta}{\vartheta}
\let\eps\varepsilon
\newcommand{\wwhat}[1]{\widehat{\widehat{#1}}}

\DeclareMathOperator{\cov}{Cov}
%\DeclareMathOperator{\skew}{Skew}
\DeclareMathOperator{\kurt}{Kurt}

@@

We continue with basic definitions that pertain to angular observables, and our
results in the subsequent sections. Let $\thvec = (\theta_1, \dots \theta_N)$ denote the set of all
angles, and let $\nuvec = (\nu_1, \dots \nu_M)$ denote the set of all
other non-angular kinematic variables needed to fully specify the
final state of the process under study. For example, $\nuvec$ may
include invariant masses or center-of-mass energies. We define an
angular observable $S_i$ as a coefficient in the probability density
function (PDF) of the process by means of
\begin{align}
    \label{eq:def-P}
    P(\nuvec, \thvec) \equiv \sum_i S_i(\nuvec) \times f_i(\thvec)\,.
\end{align}
Here, the dependence on the $n$ decay angles $\thvec$ has been
explicitly factored out in terms of the angular functions
$\{f_i(\thvec)\}$. We assume there exists a dual basis of functions
$\{\dual{f}_i(\thvec)\}$ such that the orthonormality relations
\begin{equation}
    \label{eq:def-ortho-rel}
    \int_\Omega \rmdx{^N \theta} \dual{f}_i(\thvec) f_j(\thvec)  = \delta_{ij}
\end{equation}
hold with $\Omega$ representing the full angular phase space relevant
to the process.  For particle decays, $P$ is generally expressed in
terms of the fully differential decay width,
\begin{align}
    \label{eq:def-P-decay}
    P(\nuvec, \thvec) \equiv \frac{1}{\Gamma}\frac{\rmdx{^{N+M}\Gamma}}{\rmdx{\nu_1} \dots \rmdx{\nu_M} \rmdx{\theta_1} \dots \rmdx{\theta_N}}\,,
\end{align}
where $\Gamma$ is the total decay width. For a scattering process, one can similarly use
\begin{align}
    \label{eq:def-P-scattering}
    P(\nuvec, \thvec) \equiv \frac{1}{\sigma}\frac{\rmdx{^{N+M}\sigma}}{\rmdx{\nu_1} \dots \rmdx{\nu_M} \rmdx{\theta_1} \dots \rmdx{\theta_N}}\,,
\end{align}
where the total cross section $\sigma$ is used for the
normalization. Since the determination of the total decay width or
total cross section can be quite difficult, we emphasize that
different normalizations for $P$ can be used.  For instance, the total
decay width (or cross section) of the process of interest can be
replaced by the corresponding quantity of a control-channel
process. This change of normalization is equivalent to a linear rescaling of
the angular observables $\lbrace S_i\rbrace$; thus ratios or similar suitable combinations
of the angular observables are invariant.\\

% Our method is closely related to Pearson's method of moments
% \citeneeded{}. One draws samples from a PDF $P(x | \nuvec)$ that
% depends on parameters $\nuvec$. Then one approximates the population
% (central) moments $x^k$ by the sample moments
Our method is an extension of the classical method of moments with
orthogonal functions~\cite[sec. 8.2]{James:2006zz}. The only difference
is that conventionally the angular functions are assumed
\emph{self-dual}, $\dual{f}_i = f_i$. However, it suffices that the
system of angular functions $\{f_i(\thvec)\}$ \emph{can} be transformed into
an orthonormal basis. It turns out to be much more convenient to work
in the basis natural to each process but the statistical properties
are equivalent for both approaches provided that one replace $f_i \to
\dual{f}_i$ appropriately. Using the ansatz
\begin{equation}
  \label{eq:dual-ansatz}
  \dual{f}_i = \sum_{j} a_{ij} f_j \,,
\end{equation}
the dual basis needs to be worked out case by case through solving the
linear system of equations (\ref{eq:def-ortho-rel}). For a selection
of hadron decays with a $b$ quark in the initial state and two leptons
in the final state, we list the dual bases in a series of appendices
\ref{app:btokll} through \ref{app:lambdabtolambdall}. Note that a
similar analysis was done in~\cite{Dighe:1998vk} for the decays $B \to
J/\psi \phi$ and $B \to J/\psi K^{*}$.

@@

The orthonormality relations \refeq{def-ortho-rel} imply that a single angular observable $S_i$
can be projected out of the full PDF $P$ by means of
\begin{equation}
    \label{eq:det-Pi-analytical}
    S_i(\nuvec) = \int_{\Omega} \rmdx{^N \theta}  P(\nuvec, \thvec) \dual{f}_i(\thvec)\,.
\end{equation}
where $\lbrace \dual{f}_i \rbrace$ denotes a \emph{dual basis} of angular functions. In general, $\lbrace \dual{f}_i \rbrace$ may differ from $\lbrace f_i \rbrace$. This is the
case for our selection of applications in appendices \ref{app:btokll} through \ref{app:lambdabtolambdall}.\\

It is sensible to refer to the angular observable $S_i$ as the \emph{$f_i$-moment} of the PDF $P$.
We emphasize that a relation of type \refeq{det-Pi-analytical} holds for any combination of
scalar product and orthonormal basis of angular functions $\lbrace f_i \rbrace$; \ie, there is no unique
basis of angular functions. For the proof we refer to ref. \cite{Dighe:1998vk}.\\
In addition, integration over the non-angular variables yields
\begin{equation}
    \langle S_i\rangle
    \equiv \int \rmdx{^M \nu} S_i(\nuvec)
    = \int \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N \theta} P(\nuvec,\thvec) \dual{f}_i(\thvec) \right].
\end{equation}
The remainder of this section describes the method of moments, in which we replace the
analytical integration \refeq{det-Pi-analytical} by Monte Carlo (MC) estimators.\\

The central tenet of MC integration is the fact that the expectation value $E_P[g]$ of some function
$g(x)$ under the probability density $P(x)$,
\begin{equation}
    E_P[g] \equiv \int \rmdx{x} P(x) g(x)
\end{equation}
can be approximated \cite{MCSM-2004} by the consistent and unbiased
estimator $\est{E_P[g]}$~\cite[sec. 8.2]{James:2006zz}
\begin{equation}
    \label{eq:mc-id}
    E_P[g] \to \widehat{E_P[g]} \equiv \frac{1}{K} \sum_{k=1}^K g(x^{(k)}) \,,\,    x^{(k)} \sim P
\end{equation}
due to the strong law of large numbers for $K \to \infty$ assuming
that the variates $x^{(k)}$, $k = 1, \dots, K$ are distributed as
$P$.
Throughout this letter we denote all MC estimators with a wide hat.\\

Application of \refeq{mc-id} then yields
\begin{equation}
    \langle S_i\rangle \to \widehat{\langle S_i\rangle} = \frac{1}{K} \sum_{k=1}^{K} \dual{f}_i(x^{(k)})\,.
\end{equation}
It is often of interest to obtain the $\nuvec$- observables integrated
over certain ranges of $\nuvec$; i.e., binned measurements of $\langle
S_i\rangle$.
Therefore, we introduce the bin-integrated quantity
\begin{align}
    \langle S_i\rangle_{\vec{a},\vec{b}}
    & = \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} S_i(\nuvec)\\
    & = \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta} P(\nuvec,\thvec) \dual{f}_i(\thvec)  \right]\\
    & = \int \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta}  P(\nuvec,\thvec) \dual{f}_i(\thvec)
        \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,
        \right],
\end{align}
where the argument of the indicator function $ \mathbf{1}(\vec{a} \le
\nuvec \le \vec{b})$ is to be interpreted componentwise.
Application of \refeq{mc-id} immediately yields
\begin{equation}
    \label{eq:bin-importance}
    \widehat{\langle S_i\rangle_{\vec{a},\vec{b}}}
    = \frac{1}{K} \sum_{k=1}^{K} \dual{f}_i(x^{(k)})         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
\end{equation}
This reduces the estimation of $\aver{S_i}_{\vec{a},\vec{b}}$ to a
(weighted) counting experiment. In the limit $N \to \infty$, the
central limit theorem (CLT) implies that the random vector
\begin{equation}
  \label{eq:angular-obs-vec}
  \widehat{\vec{S}_{\vec{a},\vec{b}}} \equiv (\aver{S_1}_{\vec{a},\vec{b}}\,, \dots, \aver{S_i}_{\vec{a},\vec{b}}\,,
  \dots)
\end{equation}
 follows a multivariate Gaussian distribution whose mean vector
is approximated by \refeq{bin-importance} and whose covariance is
estimated as
\begin{equation}
    \cov[\aver{S_i},\aver{S_j}]_{\vec{a},\vec{b}} \to \est{\cov}[\aver{S}_i, \aver{S}_j]_{\vec{a},\vec{b}}
        = \frac{1}{K - 1} \sum_{k=1}^{K} \big[\dual{f}_i(x^{(k)}) - \est{\langle S_i\rangle_{\vec{a},\vec{b}}}\big]\,\big[\dual{f}_j(x^{(k)}) - \widehat{\langle S_j\rangle_{\vec{a},\vec{b}}}\big]
        \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
\end{equation}
In our physics applications, the parameter space is compact and each
$\dual{f}_i$ is bounded. Hence the requisites for the most basic
version of the CLT to hold --- finite mean and covariance of
$\dual{f}_i$ --- are automatically satisfied.  We would like to
emphasize that the sample covariance should \fred{``Should'' as in it
  does in practice? Reference toy studies below} rapidly converge
towards the true covariance matrix.  We propose to declare convergence
\fred{I'd prefer: check that skewness and kurtosis are sufficiently
  small} once estimators for skewness and kurtosis are sufficiently
small,
\begin{equation}
    \est{\operatorname{Skew}}[\aver{S_i},\aver{S_j}] \ll 1\,\,\text{ and }\,\,\est{\kurt}[\aver{S_i},\aver{S_j}] \ll 1\,.
\end{equation}

Compared to the usual maximum-likelihood approach, we find for the method of moments:
\begin{enumerate}
\item The angular observable $\aver{S_i}$ can be determined
  independently of any other observable $\aver{S_j}$. It is therefore
  much more robust to physics assumptions needed to define the full
  likelihood. In particular, this means one does not have to be
  specific regarding the form of new-physics contributions.
\item It is superior for a small number of samples $N$. Likelihood
  fits tend to be numerically unstable if lots of parameters need to
  be estimated from sparse data. This is more severe if the mode of
  the likelihood is near the boundary of the physically allowed
  region.\fred{Is there some LHCb note we could cite?} In many of the
  decays of interest, there are only say dozens of events recorded.
\item The estimate is unbiased for any $N$. In contrast, the
  maximum-likelihood estimate has a bias of order
  $1/N$~\cite{Cox:1968}. In practice, one should keep in mind the
  bias-variance trade-off: it is a well known phenomenon that removing
  the bias usually leads to an increase in variance of the sampling
  distribution of the estimator~\cite[sec. 7.3]{James:2006zz}. From a
  Bayesian decision-theory point of view, both contribute similarly to
  the expected loss associated with deciding on just one value of the
  unknown parameter. It is therefore highly questionable to reduce
  only the bias~\cite[sections 13.8,17.2]{jaynes:2003}. In fact, for
  the results discussed below in \refsec{numerics}, the likelihood
  fits --- if they converge --- produce uncertainties (10--15)\%
  smaller than those from the method of moments.
\item The approximate normal distribution allows easier and more
  correct transfer of the information in the data to interested
  theorists for more accurate fits of standard-model and new-physics
  parameters \citeneeded\fred{Our fits and others'?} or for more precise predictions of
  optimized observables; e.g.,
  \cite{Egede:2008uy,Egede:2010zc,Bobeth:2010wg,Becirevic:2011bp,
    Bobeth:2012vn,Matias:2012xw,DescotesGenon:2012zf} for definitions
  of such optimized observables in $B\to K^*\ell^+\ell^-$ decays,
  \cite{Faller:2013dwa} for application to the decay $B\to
  \pi\pi\ell^-\bar\nu_\ell$, and \cite{Boeer:2014xx} for observables
  in $\Lambda_b\to\Lambda(\to N\pi)\ell^+\ell^-$). While the
  likelihood also approaches a multivariate Gaussian as $N \to
  \infty$, the two methods differ in their utility as input for
  theorists if $\widehat{\vec{S}_{\vec{a},\vec{b}}}$ is not well
  inside the physical region. For example, suppose there are two
  angular observables that are constrained to a triangular region by
  phase-space or unitarity arguments as \fred{Could add a sketch. It
    is supposed to resemble $A_{\text{FB}},F_L$ for $B \to K^* \ell \ell$.}
  \begin{equation}
    \label{eq:constr-ex}
    |S_1| + S_2 \le 1, \, S_1 \in [-1,1],\, S_2 \in [0,1] \,.
  \end{equation}
  It may (and often does) happen in practice that
  $\widehat{\vec{S}_{\vec{a},\vec{b}}}$ is close or even outside the
  allowed region such that a significant part of the probability mass
  of $\vec{S}$ covers unphysical values. In a Bayesian fit, one would
  take $\mathcal{N}(\vec{S} | \widehat{\vec{S}_{\vec{a},\vec{b}}},
  \widehat{\Sigma})$ as the sampling distribution of the ``data'', and
  simply set a uniform prior on the triangle defined by
  \refeq{constr-ex} to have a well defined problem. This could be
  trivially combined with other independent information in a global
  fit. For a likelihood fit, the constraint needs to be built in by
  the experiment into the analysis of the actual events and the
  resulting likelihood as a function of $\vec{S}$ is distinctly not
  Gaussian. Since experimental collaborations as a whole tend to favor
  data-privacy over accurate use of their results in theorist's
  analyses, the multivariate likelihood is kept secret, and cannot be
  recovered from the numerical value of $\vec{S}$ and the standard
  errors reported in written publications. The theorist then usually
  includes the results as independent measurements with a Gaussian
  distribution and disregards the constraint altogether. This last
  situation is undesirable for both experimentalists and theorists.
\end{enumerate}

@@

The dual basis $\lbrace \dual{f}_i\rbrace$ reads
\begin{equation}
\begin{aligned}
    \dual{f}_1 & = \frac{9}{8} - \frac{15}{8}\cos^2\theta_1\,, &
    \dual{f}_2 & = \frac{3}{2}\cos\theta_1\,, &
    \dual{f}_3 & = -\frac{15}{8} + \frac{45}{8}\cos^2\theta_1\,,
\end{aligned}
\end{equation}
such that
\begin{equation}
    \int_0^\pi \rmdx{\theta_1} \dual{f}_i(\theta_1) P(q^2, \theta_1) = S_i(q^2)\,.
\end{equation}

@@

The dual basis reads
\begin{equation}
\begin{aligned}
    \dual{f}_{1s} & = \frac{\big( 63 \sin^2\theta_2 - 42 \cos^2\theta_2\big) + \big(  45 \sin^2\theta_2 - 30 \cos^2\theta_2\big)\cos 2\theta_1}{64} \,,\\
    \dual{f}_{1c} & = \frac{\big(-21 \sin^2\theta_2 + 84 \cos^2\theta_2\big) + \big( -15 \sin^2\theta_2 + 60 \cos^2\theta_2\big)\cos 2\theta_1}{32} \,,\\
    \dual{f}_{2s} & = \frac{\big( 45 \sin^2\theta_2 - 30 \cos^2\theta_2\big) + \big(+135 \sin^2\theta_2 - 90 \cos^2\theta_2\big)\cos 2\theta_1}{64} \,,\\
    \dual{f}_{2c} & = \frac{\big(-15 \sin^2\theta_2 + 60 \cos^2\theta_2\big) + \big( -45 \sin^2\theta_2 +180 \cos^2\theta_2\big)\cos 2\theta_1}{32} \,,
\end{aligned}
\end{equation}
as well as
\begin{equation}
\begin{aligned}
    \dual{f}_{1i} & = \frac{\big(21 + 15 \cos1\theta_2\big)\cos\theta_2}{16}               \,,&
    \dual{f}_{2i} & = \frac{\big(15 + 45 \cos1\theta_2\big)\cos\theta_2}{16}               \,,\\
    \dual{f}_{3}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \cos2\theta_3}{32}                \,,& &\\
    \dual{f}_{4}  & = \frac{75 \sin 2\theta_2 \sin 2\theta_1 \cos \theta_3}{32}                \,,&
    \dual{f}_{4i} & = \frac{15 \sin  \theta_2 \sin 2\theta_1 \cos \theta_3}{8}                 \,,\\
    \dual{f}_{5}  & = \frac{15 \sin 2\theta_2 \sin  \theta_1 \cos \theta_3}{8}                 \,,&
    \dual{f}_{5i} & = \frac{3  \sin  \theta_2 \sin  \theta_1 \cos \theta_3}{2}                 \,,\\
    \dual{f}_{6s} & = \frac{\big( 9\sin^2\theta_2 -  6 \cos^2\theta_2\big)\cos\theta_1}{4} \,,&
    \dual{f}_{6c} & = \frac{\big(-3\sin^2\theta_2 + 12 \cos^2\theta_2\big)\cos\theta_1}{2} \,,\\
    \dual{f}_{7}  & = \frac{15 \sin 2\theta_2 \sin  \theta_1 \sin \theta_3}{8}                 \,,&
    \dual{f}_{7i} & = \frac{3  \sin  \theta_2 \sin  \theta_1 \sin \theta_3}{2}                 \,,\\
    \dual{f}_{8}  & = \frac{75 \sin 2\theta_2 \sin 2\theta_1 \sin \theta_3}{32}                \,,&
    \dual{f}_{8i} & = \frac{15 \sin  \theta_2 \sin 2\theta_1 \sin \theta_3}{8}                 \,,\\
    \dual{f}_{9}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \sin2\theta_3}{32}                \,.\\
\end{aligned}
\end{equation}
such that
\begin{equation}
    \int_0^\pi \rmdx{\theta_1} \int_0^\pi \rmdx{\theta_2} \int_0^{2\pi} \rmdx{\theta_3} \dual{f}_k(\theta_1,\theta_2,\theta_3) P(q^2, \theta_1,\theta_2,\theta_3) = S_k(q^2)\,.
\end{equation}
